\documentclass{article}
\usepackage[dvipsnames]{xcolor}
\usepackage[normalem]{ulem}

\title{\Huge\textbf{Node Messenger}\\
		\huge{Problem Statement - Group 24}}
\author{Ahmed, Tasin\hspace{1cm}Patel, Shardool\hspace{1cm}Elemary, Omar \\
		400052747\hspace{2cm}400080843\hspace{2cm}400100169}
\bigskip
\begin{document}
\maketitle
  	
\begin{table}[hp]
\begin{center}
\label{tab:}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{DATE} & \textbf{Version} & \textbf{Description} & \textbf{Edited By}\\
\hline
September 21, 2018 & 0 & Initial Draft & Ahmed, Tasin\\
\hline
September 21, 2018 & 0 & Initial Draft & Patel, Shardool\\
\hline
September 21, 2018 & 0 & Initial Draft & Elemary, Omar\\
\hline
November 25, 2018 & 1 & Final Copy & Elemary, Omar\\
\hline
November 25, 2018 & 1 & Final Copy & Ahmed, Tasin\\
\hline
November 25, 2018 & 1 & Final Copy & Patel, Shardool\\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}
	\newpage
	\newpage
	\section{Problem Statement}
	\subsection{What problem are you trying to solve?}
    As the world becomes increasingly more connected through the internet, many common internet users are looking for an easy way to communicate with each other or reach out to distant loved ones. The market for messengers has become saturated with products that put the goal of earning maximum revenue over the needs of the consumer. Our team’s focus is to gauge consumer interest by implementing a free and accessible web application messenger that allows them to \sout{personalize their experience and} chat with other users in a simple, clean and non-intrusive way. Node messenger will become a haven for users searching for a consumer-friendly product with great functionality \sout{and cross-platform support}.
	\subsection{Why is this an important problem?}
    Communication is a very important part of human evolution. \sout{We have communicated with others for thousands of years}. Today, \textcolor{red}{it} is easier than ever \textcolor{red}{to stay connected with others around us or outside our circle} \textcolor{red}{through} the increasing popularity of the internet. With the click of a button, we are able to transfer our thoughts to the opposite side of the earth. There are a lot of messaging applications available for people to choose from. However, most popular messaging applications become bloated and \textcolor{red}{intrusive} after using it for a certain period of time. Our messaging application aims to be fast and easy to use for all our users. \sout{We will also be adding features that make it different and unique compared to most other messaging applications available on the market.}
      
	\subsection{What is the context of the problem you are solving?}   
Node messenger will serve as a general purpose chat application that also supports group chats. The primary stakeholders will, therefore, be the consumers. Mainly, the people who want to connect with friends and family, various discussion groups and collaborative teams. Apart from the consumers, other stakeholders will be the current and the future developers who might want to build upon this open source project. Considering the variety of consumers that might use this application, we have to ensure that they can easily access it. Which is why Node messenger will be available on the web. Any device with a web browser should be able to access the application. Being a general purpose software with great accessibility will make the software suitable in any commercial or personal environments.
\end{document}